Teaching Dossier

### 2019-11-18 CUT/teaching-philosophy.tex
Questioning strategies complete

On questioning strategies and problem solving frameworks.

\subsection{Outside Lecture}

>>>>

\paragraph{Questioning Strategies}Between the pre-test and the outline review lies the bulk of the lecture time to be used to deliver content. I like to give my lectures using a high density of questions for the students. This is a simple, efficient, and effective way for me create a highly interactive learning environment within the lecture. Sometimes it can be difficult to get students to open up and get used to the amount of spoken input I expect from them during the lecture. I have developed some techniques for increasing my success rate with using frequent student questioning.

The first is to set the precedent early. I mean this in two senses. I start using questioning from the first day of lecture, and make sure to heavily ask student questions every single lecture. This is much easier than switching to this technique part way through the semester, or not doing for a few lectures, then having an interactive lecture. Once the students adapt to the routine of the interactive lecture they will be more comfortable answering questions, and even come to expect to be given the opportunity for input. I also mean to set a precedent on the lecture scale. Once I start delivering the lecture material, I am looking for the earliest opportunity to throw a question at the students. Usually this is immediately after the first definition or example I present. This gets the students focused on actively engaging with the material and responding early in the lecture, and builds momentum that can be carried through the entire session. As an instructor, when I get in the habit of constantly looking for the nearest opportunity to ask a question, I find my lectures are far more interesting for the students and their depth of understanding increases significantly.

On a question-by-question level it can be difficult to coax responses out of students. It is important that I ensure I wait sufficiently long for students to respond. I use a ten second count in my head, or take a sip of water, to make sure I'm pausing long enough for a student to both work out the answer and work up the confidence to respond. Most of the time no hands go up immediately, but after a waiting period some hands will go up. Although sometimes students are not responding because they genuinely do not know the answer. When I get a sense this is happening, I will break the question down for them into smaller and easier parts. At some level I will find something simple enough that someone in the class will know the answer and be willing to respond. I prefer to not simply give the answer and move on. Although it may feel like the best thing to do to preserve momentum and save time, the fact that students are not responding means we have identified a gap in their understanding and it is important to drill down on this gap and help students bridge it piece by piece.
\subsection{Outside Lecture}
